Scottish Child Payment Interventions

### 2024-01-19 minos/outcomes/SCP_vis.Rmd
Changing CPR vis to run on scotland scaled data

```{r}
source(here::here('minos', 'utils_datain.R'))
```

```{r}
#out.path <- here::here('output', 'default_config')
out.path <- here::here('output', 'glasgow_scaled')
#out.path <- here::here('output', 'scaled_scotland')

>>>>

```{r source_functions, include=FALSE}
source(here::here('minos', 'utils_datain.R'))
```

```{r read_data}
#out.path <- here::here('output', 'default_config')
#out.path <- here::here('output', 'glasgow_scaled')
out.path <- here::here('output', 'scaled_scotland')
